\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-19 icra-2021.tex
added overview figure and addressed some of the Hector's comments

In the spirit of reducing waste, costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}. The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a monitoring mission optimized for the craft's dynamics. The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis. Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.

@@

Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$. Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.

\begin{defn}[Mission]\label{def:mission}
  At a time instant $k\in[1,t_f)\subseteq\mathbb{R}_{\geq 1}$, the mission is defined as the ordered list
  \begin{equation}\label{eq:mission}\begin{split}
    \mathcal{M}_k:=\{(\varphi,\psi_1,...,\psi_\sigma)\mid\exists&\,\,\varphi\in\mathbb{C}_k,\,\\&\psi_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
  \end{split}\end{equation}
  where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set.
\end{defn}

The overall plan is the union of all the missions. If for simplicity the system is sampled discrete-time
\begin{equation}
  \mathcal{M}:=\bigcup_{i\in[t_f]}{\mathcal{M}_i},
\end{equation}
the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.

\subsection{Mission state}
\label{sec:model}

The mission state is the UAV's position in space and the energy evolution in time. Despite we show a linear relation between the instantaneous energy and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different. We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.

Consider the position $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$, the set
\begin{equation}\label{eq:area}
  \mathcal{P}_k:=\{\mathbf{p}_k\mid\varphi_k(\mathbf{p}_k,c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
\end{equation}
delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$).

@@

The control $\mathbf{u}$ along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}  
  \mathbf{u}_k&=\begin{bmatrix}g(\mathbf{s}_k)-g(\mathbf{s}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
  B&=\left[\begin{array}{cccc}
    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
     &            0&       &  \\
     &             & \ddots&  \\
     &             &       & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$. Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy.

@@

Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The instantaneous computational energy component can be defined
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^s:=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
\end{split}\end{equation}

@@

Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
\begin{equation}\begin{split}
  \mathrm{SoC}_k=-\left(V-
  \sqrt{
    V^2-
    4R\tilde{V}y_kV^{-1}}
  \right)/2RQ_c,\\ 
\end{split}\end{equation}
where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity. We define the output constraints set
\begin{equation}
  \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
\end{equation}
where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy.
\subsection{Deployment algorithm}

>>>>

In the spirit of reducing costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}. The mission consists of a UAV flying in circles and lines covering a polygon, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics. The algorithm plans the mission controlling the processing rate, the radius of the circles, and the distance between the lines. Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.

@@

Let a mission's stage be a generic continuous twice differentiable TEE $\varphi$ and a set of tasks $\psi_1,\dots,\psi_{\sigma}$. Moreover, let $t_f$ be the final time, $[\,\cdot\,]$ the set $\{0,1,\dots,\,\cdot\,\}$, $[\,\cdot\,]^+$ the set $\{0\}/[\,\cdot\,]$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the lower and upper bound of $\,\cdot\,$. If $\,\cdot\,$ is a value, the bounds are user defined and retrieved from a lookup table; if a set, they correspond to minimum and maximum of the set.

\begin{defn}[Stage and mission]\label{def:mission}
  At a time instant $k\in[0,t_f)$, the \emph{stage} is defined as the ordered list
  \begin{equation}\label{eq:mission}\begin{split}
    \mathcal{M}_k:=\{(\varphi_k&(\,\cdot\,),\psi_1(\,\cdot\,),...,\psi_\sigma(\,\cdot\,))\mid\\\exists\,\,&\varphi_k(\,\cdot\,)\in\mathbb{C}_k,\,\\&\,\psi_i(\,\cdot\,)\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
  \end{split}\end{equation}
  where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set. The parameters of the TEE $\varphi_k$ are defined in Subsection~\ref{sec:model}, of the tasks $\psi_1,\dots,\psi_\sigma$ in~\ref{sec:computations-model}.

  The \emph{mission} is the union of all the stages, along with a function $\lambda:\mathbb{R}^2\rightarrow\mathcal{M}_k$ which maps a point $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$ to a specific stage. If for simplicity the system is sampled discrete-time
  \begin{equation}
    \mathcal{M}:=(\lambda(\mathbf{p}),\bigcup_{i\in[t_f]}{\mathcal{M}_i}),
  \end{equation}
  the algorithm inputs $\mathcal{M}_k$ and outputs the position, the instantaneous energy consumption, and the controls sequence--an action performed evolving the mission state.
\end{defn}

\begin{figure}[t]
  \centering
  \input{\figpath/icra-2021_overview.tikz}
  \caption{Overview}
  \label{fig:overview}
\end{figure}

\subsection{State: position and energy}
\label{sec:model}

The state is the UAV's position in space and the energy evolution in time. Despite we show a linear relation between the instantaneous energy consumption and the energy evolution (Theorem~\ref{thm:state-vs-energy}), the two are different. We show after the main results how such approach indeed allowed us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.

Consider the position $\mathbf{p}$, the set
\begin{equation}\label{eq:area}
  \mathcal{P}_k:=\{\mathbf{p}_k\mid\varphi_k(\mathbf{p}_k,c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
\end{equation}
delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$).

@@

The control $\mathbf{u}$ along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}  
  \mathbf{u}_k&=\begin{bmatrix}g(\mathbf{s}_k)-g(\mathbf{s}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
  B&=\left[\begin{array}{cccc}
    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
     &            0&       &  \\
     &             & \ddots&  \\
     &             &       & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{1}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$. Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy consumption.

@@

Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous computational energy consumption value obtained interrogating \powprof{}
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^s:=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
\end{split}\end{equation}

@@

Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
\begin{equation}\begin{split}
  \mathrm{SoC}_k=-\left(V-
  \sqrt{
    V^2-
    4R\tilde{V}y_kV^{-1}}
  \right)/2RQ_c,\\ 
\end{split}\end{equation}
where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity. We define the output constraints set
\begin{equation}
  \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
\end{equation}
where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy consumption.
\subsection{Deployment algorithm}
